---
title: "Module 8"
author: "Emily Yang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Challenge 1

```{r Challenge 1}
#library(manipulate)
#outcomes <- c(1, 2, 3, 4, 5, 6)
#manipulate(hist(sample(outcomes, n, replace = TRUE), breaks = c(0.5, 1.5, 2.5,
#    3.5, 4.5, 5.5, 6.5), probability = TRUE, main = paste("Histogram of Outcomes of ",
#    n, " Die Rolls", sep = ""), xlab = "roll", ylab = "probability"), n = #slider(0,
 #   10000, initial = 100, step = 100))

#nrolls <- 1000
#roll <- function(x) {
 #   sample(1:6, x, replace = TRUE)
#}
#two_dice <- roll(nrolls) + roll(nrolls)
#hist(two_dice, breaks = c(1.5:12.5), probability = TRUE, main = "Rolling Two Dice",
#    xlab = "sum of rolls", ylab = "probability")

```
## Challenge 2
What is the probability that you draw a face card? 12/52 <br>

What is the probability that you draw a King? 4/52

What is the probability that you draw a spade? 13/52

What is the probability that you draw a spade given that you draw a face card? 3/12

What is the probability that you draw a King given that you draw a face card? 4/12

What is the probability that you draw a card that is both from a red suit (hearts or diamonds) and a face card?

Pr (A) = red suit = 26/52 = 1/2

Pr (B) = face card = 12/52 =

Pr (A | B) = red suit given face card = 6/12

Pr (A ⋂ B) = Pr (A | B) × Pr (B) = 6/12 × 12/52 = 6/52 = 0.1153846

What is the probability that you draw a card that is either a club or not a face card?

Pr (A) = club = 13/52 = 13/52
Pr (B) = not a face card = 40/52

Pr (A ⋂ B) = club and not a face card = 10/52

Pr (A ⋃ B) = Pr (A) + Pr (B) - Pr (A ⋂ B) = 13/52 + 40/52 - 10/52 = 43/52

## Challenge 3
``` {r Challenge 3}
outcomes <- c("heads", "tails")
prob <- c(1/2, 1/2)
barplot(prob, ylim = c(0, 0.6), names.arg = outcomes, space = 0.1, xlab = "outcome",
    ylab = "Pr(X = outcome)", main = "Probability Mass Function")
```
