---
title: "Module 8"
author: "Emily Yang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Challenge 1
Paste directly into console to get slider. eval=FALSE knits manipulate functions
```{r Challenge 1, eval=FALSE}
library(manipulate)
outcomes <- c(1, 2, 3, 4, 5, 6) #replace = TRUE lets you pick the same number multiple times. 
manipulate(hist(sample(outcomes, n, replace = TRUE), breaks = c(0.5, 1.5, 2.5,
    3.5, 4.5, 5.5, 6.5), probability = TRUE, main = paste("Histogram of Outcomes of ",
    n, " Die Rolls", sep = ""), xlab = "roll", ylab = "probability"), n = slider(0, 10000, initial = 100, step = 100))

nrolls <- 1000
roll <- function(x) {
   sample(1:6, x, replace = TRUE)
}
two_dice <- roll(nrolls) + roll(nrolls)
hist(two_dice, breaks = c(1.5:12.5), probability = TRUE, main = "Rolling Two Dice",
    xlab = "sum of rolls", ylab = "probability")

```
## Challenge 2
What is the probability that you draw a face card? 12/52

What is the probability that you draw a King? 4/52

What is the probability that you draw a spade? 13/52

What is the probability that you draw a spade given that you draw a face card? 3/12

What is the probability that you draw a King given that you draw a face card? 4/12

What is the probability that you draw a card that is both from a red suit (hearts or diamonds) and a face card?

Pr (A) = red suit = 26/52 = 1/2

Pr (B) = face card = 12/52 =

Pr (A | B) = red suit given face card = 6/12

Pr (A ⋂ B) = Pr (A | B) × Pr (B) = 6/12 × 12/52 = 6/52 = 0.1153846

What is the probability that you draw a card that is either a club or not a face card?

Pr (A) = club = 13/52 = 13/52
Pr (B) = not a face card = 40/52

Pr (A ⋂ B) = club and not a face card = 10/52

Pr (A ⋃ B) = Pr (A) + Pr (B) - Pr (A ⋂ B) = 13/52 + 40/52 - 10/52 = 43/52

## Challenge 3
``` {r Challenge 3}
outcomes <- c("heads", "tails")
prob <- c(1/2, 1/2)
barplot(prob, ylim = c(0, 0.6), names.arg = outcomes, space = 0.1, xlab = "outcome",
    ylab = "Pr(X = outcome)", main = "Probability Mass Function")
cumprob <- cumsum(prob)
barplot(cumprob, names.arg = outcomes, space = 0.1, xlab = "outcome", ylab = "Cumulative Pr(X)",
    main = "Cumulative Probability")
outcomes <- c(1, 2, 3, 4, 5, 6)
prob <- c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6)
barplot(prob, ylim = c(0, 0.5), names.arg = outcomes, space = 0.1, xlab = "outcome",
    ylab = "Pr(X = outcome)", main = "Probability Mass Function")
```
## Beta Distribution 
```{r Challenge 4, eval=FALSE}
library(ggplot2)
a <- 2
b <- 1
K <- 2
x <- seq(from = 0, to = 1, by = 0.025)
fx <- K * x^(a - 1) * (1 - x)^(b - 1)
lower_x <- seq(from = -0.25, to = 0, by = 0.025)  # add some values of x less than zero
upper_x <- seq(from = 1, to = 1.25, by = 0.025)  # add some values of x greater than one
lower_fx <- rep(0, 11)  # add fx=0 values to x<0
upper_fx <- rep(0, 11)  # add fx=0 values to x>1
x <- c(lower_x, x, upper_x)  # paste xs together
fx <- c(lower_fx, fx, upper_fx)  # paste fxs together
d <- as.data.frame(cbind(x, fx))
p <- ggplot(data = d, aes(x = x, y = fx)) + xlab("x") + ylab("f(x)") + geom_line()
p

library(manipulate)
manipulate(ggplot(data = d, aes(x = x, y = fx)) + xlab("x") + ylab("f(x)") +
    geom_line() + geom_polygon(data = data.frame(xvals = c(0, n, n, 0), fxvals = c(0,
    K * n^(a - 1) * (1 - n)^(b - 1), 0, 0)), aes(x = xvals, y = fxvals)) + ggtitle(paste("Area Under Function = ",
    0.5 * n * K * n^(a - 1) * (1 - n)^(b - 1), sep = " ")), n = slider(0, 1,
    initial = 0.5, step = 0.01))
x <- seq(from = 0, to = 1, by = 0.005)
prob <- 0.5 * x * K * x^(a - 1) * (1 - x)^(b - 1)
barplot(prob, names.arg = x, space = 0, main = "Cumulative Probability", xlab = "x",
    ylab = "Pr(X ≤ x)")
pbeta(0.75, 2, 1)  # cumulative probability for x ≤ 0.75

pbeta(0.7, 2, 1)  # yields .49
qbeta(0.49, 2, 1)  # yield 0.7
```

