---
title: "Module 8"
author: "Emily Yang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Challenge 1

```{r Challenge 1}


```
## Challenge 2
What is the probability that you draw a face card? 12/52 <br>

What is the probability that you draw a King? 4/52

What is the probability that you draw a spade? 13/52

What is the probability that you draw a spade given that you draw a face card? 3/12

What is the probability that you draw a King given that you draw a face card? 4/12

What is the probability that you draw a card that is both from a red suit (hearts or diamonds) and a face card?

Pr (A) = red suit = 26/52 = 1/2

Pr (B) = face card = 12/52 =

Pr (A | B) = red suit given face card = 6/12

Pr (A ⋂ B) = Pr (A | B) × Pr (B) = 6/12 × 12/52 = 6/52 = 0.1153846

What is the probability that you draw a card that is either a club or not a face card?

Pr (A) = club = 13/52 = 13/52
Pr (B) = not a face card = 40/52

Pr (A ⋂ B) = club and not a face card = 10/52

Pr (A ⋃ B) = Pr (A) + Pr (B) - Pr (A ⋂ B) = 13/52 + 40/52 - 10/52 = 43/52